Using traffic analysis to identify The Second Generation Onion Router

### 2011-06-13 ieee-conference-paper/paper.tex
Remove phone numbers

\author{
  \IEEEauthorblockN{John Barker}
  \IEEEauthorblockA{
  School of Computer and\\Security Science\\
  Edith Cowan University\\
  Mt Lawley, Western Australia\\
  Email: john.barker@our.ecu.edu.au}
  \and
  \IEEEauthorblockN{Peter Hannay}
  \IEEEauthorblockA{
  School of Computer and\\Security Science\\
  Edith Cowan University\\
  Mt Lawley, Western Australia\\
  Email: p.hannay@ecu.edu.au\\
  Telephone: (08) 9370 6374}
  \and
  \IEEEauthorblockN{Patryk Szewczyk}
  \IEEEauthorblockA{
  School of Computer and\\Security Science\\
  Edith Cowan University\\
  Mt Lawley, Western Australia\\
  Email: p.szewczyk@ecu.edu.au\\
  Telephone: (08) 9370 6979\\
  Fax: (08) 9370 6100}
}

>>>>

\author{
  \IEEEauthorblockN{John Barker}
  \IEEEauthorblockA{
  School of Computer and\\Security Science\\
  Edith Cowan University\\
  Mt Lawley, Western Australia\\
  Email: john.barker@our.ecu.edu.au}
  \and
  \IEEEauthorblockN{Peter Hannay}
  \IEEEauthorblockA{
  School of Computer and\\Security Science\\
  Edith Cowan University\\
  Mt Lawley, Western Australia\\
  Email: p.hannay@ecu.edu.au}
  \and
  \IEEEauthorblockN{Patryk Szewczyk}
  \IEEEauthorblockA{
  School of Computer and\\Security Science\\
  Edith Cowan University\\
  Mt Lawley, Western Australia\\
  Email: p.szewczyk@ecu.edu.au}
}
